---
title: "Data Analysis"
author: "Fabiano Araujo"
format: html
editor: visual
---

## Introduction

This report starts with descriptive statistics and then presents the results of paired t-tests and repeated measures ANOVA conducted on Likert-scale responses before and after an intervention.

### Descriptive Statistics

```{r message=FALSE, warning=FALSE, include=TRUE}
#| echo: false
source("data_analysis.R")
```

```{r}
#| echo: false
#| warning: false
library(gt)
descriptive_table <- descriptive_summary %>%
  gt() %>%
  fmt_number(
    columns = c(mean, sd, variance),
    decimals = 2
  ) %>%
  fmt_number(
    columns = c(median, min, max),
    decimals = 0
  ) %>%
  cols_label(
    n = "count",
    sd = "std dev",
  )

descriptive_table
```

### Paired t-tests results

A paired t-test compares the mean scores between the pre-test and post-test for each question.

**Interpreting the t-value:** Magnitude: A larger absolute t-value indicates a greater difference between the means, suggesting a stronger evidence against the null hypothesis (which usually states that there is no difference between the groups).

Sign: The sign of the t-value (positive or negative) indicates the direction of the difference between the means.

```{r}
#| echo: false
t_test_table <- t_test_results %>%
  select(question, t_statistic, degrees_freedom, p_value) %>%
  gt() %>%
  tab_header(
    title = "Paired t-test results",
  ) %>%
  fmt_number(
    columns = c(t_statistic),
    decimals = 2
  ) %>%
  fmt_number(
    columns = c(p_value),
    decimals = 4
  ) %>%
  fmt_number(
    columns = c(degrees_freedom),
    decimals = 0
  ) %>%
  tab_style(
    style = cell_text(weight = "bold", color = "red"),
    locations = cells_body(
      columns = c(p_value),
      rows = p_value < 0.05
    )
  )

t_test_table
```

## References

G. Norman, Likert scales, levels of measurement and the “laws” of statistics, Adv. Heal. Sci. Educ. 15 (2010) 625–632. [https://doi.org/10.1007/s10459-010-9222-y](https://doi.org/10.1007/s10459-010-9222-y){target="_blank"}.
  
  
